### 2015-03-26 text/appendix_denotational.tex
Definition of a transformation rule

@@

\begin{example}{Pattern}
For the Stations Rule in Figure \ref{fig:dsltransformation}, the corresponding pattern is
$(S_O,S_G,T)$ where $S_O$ represents the set of all station instances from the orgnization language, $S_G$, the corresponding set of the gender language, and $T$ the set of a trace links between a pair of instances.
\end{example}

@@

\begin{example}{Instance Graph}
Again, using the Stations Rule in Figure \ref{fig:dsltransformation}, the set of corresponding instance graphs is $\{ ( \{ s_o, s_t \} , \{  \} ) \mid \}$
$(S_O,S_G,T)$ where $S_O$ represents the set of all station instances from the orgnization language, $S_G$, the corresponding set of the gender language, and $T$ the set of a trace links between a pair of instances.
\end{example}

>>>>

% !TEX root = ../main.tex

@@

\begin{example}
For the Stations Rule in Figure \ref{fig:dsltransformation}, the corresponding pattern is
$(S_O,S_G,T)$ where $S_O = \{ \mbox{station}_{o,1}, \mbox{station}_{o,2},\dots \}$ represents the set of all station instances from the organization language, $S_G = \{ \mbox{station}_{g,1}, \mbox{station}_{g,2},\dots \}$, the corresponding set of the gender language, and $T = S_O \times S_G$ the set of a trace links between a pair of instances.
\end{example}

@@

\begin{example}
Again, using the Stations Rule in Figure \ref{fig:dsltransformation}, the set of corresponding instance graphs is $\{ ( \{ s_o, s_g \} , \{ (s_o, s_t \} ) \mid s_o \in S_O \mbox{and} s_g \in S_G \}$. Thus, each instance graph consists of a pair of an organization station and a gender station, together with a single edge representing the trace link.
\end{example}

\begin{definition}{Transformation Rule}
A \emph{transformation rule} over a given set of vertex types $\mathcal{VT} = \mathcal{VT}^i \cup \mathcal{VT}^o$ with $ \mathcal{VT}^i \cap \mathcal{VT}^o = emptyset$ and a given set of edge types $\mathcal{ET} =  \mathcal{ET}^i \cup \mathcal{ET}^o$ with $\mathcal{ET}^i \cap \mathcal{ET}^o = \emptyset$ is a partitioned pattern, describing a transformation by distinguishing between input elements $ \mathcal{VT}^i$ and  $\mathcal{ET}^i$ and output elements $ \mathcal{VT}^o$ and  $\mathcal{ET}^o$. 
\end{definition}
